\FloatBarrier
\chapter{TPC Characterization}
\label{chap:Analysis}
\FloatBarrier

The detection principles of \gls{lxe} \glspl{tpc} are well know.
Their responses are, however, quite different depending on the materials used, geometry and location, e.g., under- or overground.
To operate this \gls{tpc} as a benchmark for other \glspl{tpc} that are tested in the \gls{xebra} platform, we have to fully understand it first.
We use known calibration sources, \gls{se} and \isotope[83][36]{Kr}, to characterize and calibrate the \gls{tpc}.

\FloatBarrier
\section{Single Electrons}
\label{sec:SE}
\FloatBarrier

A \gls{se} is the light signal we measure from just one electron that undergoes proportional scintillation in the \gls{gxe}.
As such, a \gls{se} has a characteristic signal.
We can infer a detector-specific area and width of an \gls{se}.
This helps us understand S2 signals as they are composed of multiple electrons and the same rules apply for their amplification.
With the mean area of an \gls{se}, the amplification gain $ g_\mathrm{SE} $, we can count the electrons in an S2 signal.
Furthermore, the width and rate of \gls{se} are of interest and will be examined.
First, we discuss the origin of \glspl{se} in the \gls{tpc} followed by the peak selection criteria.


\input{Chapters/sub/SingleElectrons/1source}
\newpage
\input{Chapters/sub/SingleElectrons/2tagging}
\newpage
\input{Chapters/sub/SingleElectrons/3g2}
\newpage
\input{Chapters/sub/SingleElectrons/4width}
\newpage
% \input{Chapters/sub/SingleElectrons/5rate}
\newpage

\FloatBarrier
\section{Krypton}
\label{sec:Kr}
\FloatBarrier


In the following we investigate the position dependent detector responses to scintillation light and charge which form the S1 and S2 signal.
We investigate the \gls{lce}, \gls{elt} and scintillation inhomogeneities to build corrections that allow us to infer a measure of the number of initial quanta.
The previous investigation of \glspl{se} and the subsequent measurement of the amplification gain $ g_\mathrm{SE} $ further allow us to quantify the extraction efficiency in the dual-phase \gls{tpc} of \gls{xebra}.
Another step can be the conversion to the energy scale.
The signal of a Krypton isotope, discussed in the following, is used as a calibration source for these investigations.
% depending of what else I write in the chapter, add more description here


\input{Chapters/sub/Krypton/1source}
\newpage
\input{Chapters/sub/Krypton/2tagging}
\newpage
\input{Chapters/sub/Krypton/3lce}
\newpage
\input{Chapters/sub/Krypton/4e-lifetime}
\newpage
\input{Chapters/sub/Krypton/5scint-inhomo}
\newpage
\input{Chapters/sub/Krypton/6scint-gain}
\newpage
\input{Chapters/sub/Krypton/7eng-scale}
\newpage
\input{Chapters/sub/Krypton/8bg}
\newpage
\FloatBarrier
